---
title: "LCR Variable Selection"
output: html_notebook
---

```{r}
library(label.switching)
library(BayesLogit)
library(ggplot2)
library(viridis)
source('./functions_for_BLCR_collapsed.R')
```

## Simulated data

Dean and Raftery Binary dataset, along with $\beta = (0.4, 1, 0.5, 0, 0, 0.4)$. The response variables consist of 4 (items 1-4) useful variables and 9 noise variables (items 5-13).


```{r}

p <- 5
G <- 2
n <- 500

#item probabilities 
theta1 <- matrix(c(0.6,0.4,0.2,0.8), nrow = G, byrow = TRUE)
theta2 <- matrix(c(0.8,0.2,0.5,0.5), nrow = G, byrow = TRUE)
theta3 <- matrix(c(0.7,0.3,0.4,0.6), nrow = G, byrow = TRUE)
theta4 <- matrix(c(0.6,0.4,0.9,0.1), nrow = G, byrow = TRUE)
theta5 <- matrix(c(0.5,0.5,0.5,0.5), nrow = G, byrow = TRUE)
theta6 <- matrix(c(0.4,0.6,0.4,0.6), nrow = G, byrow = TRUE)
theta7 <- matrix(c(0.3,0.7,0.3,0.7), nrow = G, byrow = TRUE)
theta8 <- matrix(c(0.2,0.8,0.2,0.8), nrow = G, byrow = TRUE)
theta9 <- matrix(c(0.9,0.1,0.9,0.1), nrow = G, byrow = TRUE)
theta10 <- matrix(c(0.6,0.4,0.6,0.4), nrow = G, byrow = TRUE)
theta11 <- matrix(c(0.7,0.3,0.7,0.3), nrow = G, byrow = TRUE)
theta12 <- matrix(c(0.8,0.2,0.8,0.2), nrow = G, byrow = TRUE)
theta13 <- matrix(c(0.1,0.9,0.1,0.9), nrow = G, byrow = TRUE)

realtheta <- list(theta1, theta2, theta3, theta4, theta5, theta6, theta7, theta8, theta9, theta10, theta11, theta12, theta13)
M <- length(realtheta)
K <- sapply(realtheta, ncol)

#Strongly informative predictor
X1 <- rnorm(n)


#X2 correlated to X1 
X2 <- 0.7*X1 + rnorm(n,0,0.2) 


#Pure noise variables
X3 <- rnorm(n)
X4 <- rnorm(n)

#less informative variable
X5 <- rnorm(n)



realbeta <- c(0.4, 1, 0.5, 0, 0, 0.4)

X <- cbind(1, X1, X2, X3, X4, X5)

mu <- X%*%realbeta

logit_prob <- exp(mu)/(1+exp(mu))

logit_prob <- cbind(logit_prob, 1-logit_prob)

class <- apply(logit_prob, 1, function(x) sample(1:G, 1, prob = x))

Y <- matrix(0,nrow = n,ncol = M)

for(i in 1:n){
  for (j in 1:M){
    theta_mat_row <- realtheta[[j]][class[i],]
    Y[i,j] <- sample(1:K[j], 1, prob = theta_mat_row)
  }
}


X <- X[,2:6]

```

## Running the sampler

Running the variable selection sampler on the simulated data. We'll do 50000 iterations, discarding 2000 for burnin, and then retain every 10th sample.

```{r}

#initialising variables

init <- initialise_variables_BLCR_collapsed(G = G, X = X, Y = Y, beta_prior_mean = c(0,0), beta_prior_var_factor = 10)

#gamma prior parameters, we'll set this so that the relevant beta is uniform.
a = 1
b = 1

list2env(init, envir = .GlobalEnv)

n_iter <- 50000
beta_samples <- array(0, dim = c(dim(beta), n_iter))
omega_samples <- array(0, dim = c(dim(omega), n_iter))
nu_samples <- array(0, dim = c(length(nu), n_iter))
z_samples <- array(0, dim = c(dim(z), n_iter))
w_samples <- array(0, dim = c(dim(w), n_iter))
gamma_samples <- array(0, dim = c(length(gamma),n_iter))
N_g_samples <- array(0, dim = c(length(N_g), n_iter))
N_gjk_samples <- array(0, dim = c(dim(N_gjk), n_iter))


for (count in 1:n_iter){
  
  gamma_up <- gamma_update(gamma = gamma, p = p, beta_prior_cov_inv = beta_prior_cov_inv, beta_prior_mean = beta_prior_mean, kappa = kappa , G = G, X_current = X_current, omega = omega, tau =  tau, X = X)
  
  list2env(gamma_up, envir = .GlobalEnv)
  
  omega <- omega_update(eta = eta, mu = mu, G = G, n = n, omega = omega)
  
  exp_mu <- exp(mu)
  
  logit_probs <- logit_probs_update(eta = eta)
  
  log_logit_probs <- log(logit_probs)
  
  C <- C_update(mu = mu, exp_mu = exp_mu, G = G, C = C)
  
  kappa <- kappa_update(z)
  
  eta <- eta_update(mu = mu, C = C)
  
  A <- A_update(kappa = kappa, omega = omega, C = C)
  
  beta_up <- beta_update(gamma = gamma, X_current = X_current, G = G, p = p, beta_prior_cov_inv = beta_prior_cov_inv, A = A, beta_prior_mean = beta_prior_mean, omega = omega)
  
  list2env(beta_up, envir = .GlobalEnv)
  
  mu <- mu_update(X = X, beta = beta)
  
  tau <- tau_update(gamma = gamma, a = a, b = b)
  
  N_up <- N_updates(z = z, Y_indicator = Y_indicator, N_jk, nu)
  
  N_g <- N_up$N_g
  
  N_gjk <- N_up$N_gjk
  
  nu <- nu_update(nu = nu, M = M, K = K, G = G, alpha = alpha, N_g, N_gjk = N_gjk, inclusion_sum = inclusion_sum, exclusion_sum = exclusion_sum, count = count)

  z_up <- z_update(z = z, nu = nu, mu = mu, K = K, alpha = alpha, N_gjk = N_gjk, N_g = N_g, n = n, G = G, Y_indicator = Y_indicator, gamma = gamma, X_current = X_current,  beta = beta, beta_cov_inv = beta_cov_inv, beta_cov_inv_chol = beta_cov_inv_chol, omega = omega, C = C)
  
  
  list2env(z_up, envir = .GlobalEnv)
  
  beta_samples[,,count] <- beta
  
  nu_samples[,count] <- nu
  
  gamma_samples[,count] <- gamma
  
  z_samples[,,count] <- z
  
  w_samples[,,count] <- w
  
  N_g_samples[,count] <- N_g
  
  N_gjk_samples[,,,count] <- N_gjk
  
  omega_samples[,,count] <- omega
  
  if(count %% 5000 == 0){
    print(paste('iteration:', count))
  }
}


```

Post processing (burnin removal, relabelling, thinning)

```{r}
#removing burnin

burnin <- 2000

burned_samples <- BLCR_varsel_burn(burnin = burnin, beta_samples = beta_samples, nu_samples = nu_samples, gamma_samples = gamma_samples, z_samples = z_samples, w_samples = w_samples, N_g_samples = N_g_samples, N_gjk_samples = N_gjk_samples, omega_samples = omega_samples)

list2env(burned_samples, envir = .GlobalEnv)

#relabelling

z_mat <- matrix(0, nrow = dim(z_samples_burned)[3], ncol = n)
for (iter in 1:dim(z_samples_burned)[3]){
  temp <- z_samples_burned[,,iter]
  temp_row <- apply(temp,1,which.max)
  z_mat[iter,] <- temp_row 
}
w_samples_reshape <- aperm(w_samples_burned,c(3,1,2))
ls <- label.switching(method = "STEPHENS", z = z_mat, K = G, p = w_samples_reshape)

ls_perm <- ls$permutations$STEPHENS

relabelled_samples <- BLCR_varsel_relabel(perm = ls_perm, beta_samples = beta_samples_burned, z_samples = z_samples_burned, w_samples = w_samples_burned, N_gjk_samples = N_gjk_samples_burned, N_g_samples = N_g_samples_burned, omega_samples = omega_samples_burned)

list2env(relabelled_samples, envir = .GlobalEnv)

#thinning

thin <- 10

thinned_samples <- BLCR_varsel_thin(thin = thin, beta_samples = relabelled_beta_samples, nu_samples = nu_samples_burned, gamma_samples = gamma_samples_burned, z_samples = relabelled_z_samples, w_samples = relabelled_w_samples, N_g_samples = relabelled_N_g_samples, N_gjk_samples = relabelled_N_gjk_samples, omega_samples = relabelled_omega_samples)

list2env(thinned_samples, envir = .GlobalEnv)

```

Now looking at the results

```{r}

#looking at the estimates and proportions

beta_mean <- apply(beta_samples_thin, c(1,2), mean)
beta_sd <- apply(beta_samples_thin, c(1,2), sd)
gamma_inclusion_proportion <- apply(gamma_samples_thin, 1, mean)
nu_inclusion_proportion <- apply(nu_samples_thin, 1, mean)

#coincidence matrix for the proportion of times item and predictor variables were included together

gamma_coincidence <- (gamma_samples_thin%*%t(gamma_samples_thin))/(dim(gamma_samples_thin)[2])
nu_coincidence <- (nu_samples_thin%*%t(nu_samples_thin))/(dim(nu_samples_thin)[2])

#Want to print out the coincidence matrices here as well as summary stats, and maybe some other diagnostics? Then I need to put in some plots like trace density etc.
cat("Covariate Inclusion Coincidence:\n", capture.output(print(gamma_coincidence[2:6,2:6])), sep="\n")
cat("Item Inclusion Proportion:\n", capture.output(print(nu_inclusion_proportion)), sep="\n")
cat("beta mean:\n", capture.output(print(beta_mean)), sep="\n")

```

Plots

```{r}
#trace plots

par(mfrow = c(3,2), mar = c(3,3,2,1))

for (i in 1:dim(beta_samples_thin)[1]) {
  plot(beta_samples_thin[i,1,], type = "l", col = "blue", main = paste("beta", i-1), xlab = "Iteration", ylab = "Value")
}


```

```{r}
#density plots


par(mfrow = c(3,2), mar = c(3,3,2,1))

for (i in 1:dim(beta_samples_thin)[1]) {
  plot(density(beta_samples_thin[i,1,]), type = "l", main = paste("beta", i-1), xlab = "Iteration", ylab = "Value")
}

```

```{r}
#heatmap for the covariate inclusion

pheatmap(gamma_coincidence[2:6,2:6], scale = "none",cluster_rows = FALSE,cluster_cols = FALSE, angle_col = 0, color = viridis(300), main  = 'Covariate Inclusion Coincidence', fontsize_row = 6, cellwidth = 60, labels_row = paste("X",1:5), labels_col = paste("X",1:5))


```
